Transitive Models of ZF

### 2022-02-26 Transitive_Models/document/root.tex
Correcting some section titles. Minor edition in abstract of document

\begin{abstract}
  We redeveloped our formalization of forcing in the set theory framework of
  Isabelle/ZF. Under the assumption of the existence of a countable
  transitive model of ZFC, we construct proper generic extensions 
  that satisfy the Continuum Hypothesis and its negation.
\end{abstract}

>>>>

\begin{abstract}
  We extend the ZF-Constructibility session, by relativizing several
  theories of Isabelle/ZF to a transitive class. This work is a
  prerrequisite to our formalization of the independence of the
  Continuum Hypothesis.
\end{abstract}
